---
title: "MATH 242 Midterm Project"
author: "Jiaxing and Gage"
date: "3/02/2024"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r}
# install.packages("leaps")
# install.packages("glmnet")
```

```{r r_packages}
#| warning: false
#| message: false
library(dplyr)
library(readr)
library(ggplot2)
library(glmnet)
library(boot)
library(gridExtra)
library(leaps)
```

```{r load_data}
nyc_condos <- read.csv("data/nyc-condos_s24.csv") 
nyc_condos_full <- read.csv("data/full_data.csv")
```

```{r split_data}
# Set the seed 
set.seed(123)
# Create an index to randomly sample 70% of the data for training
train_index <- sample(1:nrow(nyc_condos_full), 0.7 * nrow(nyc_condos_full))
# Create the training set
train_data <- nyc_condos_full[train_index, ]
# Create the testing set
test_data <- nyc_condos_full[-train_index, ]
```

```{r EDA}
#| warning: false
#| message: false
# summary of dataset
str(nyc_condos)
```

```{r variable_transformation}

# # calculate average market value for each year
# nyc_condos <- nyc_condos %>%
#   group_by(Report.Year) %>%
#   mutate(average_market_value = mean(Full.Market.Value, na.rm = TRUE))
# 
# 
# # Log transform Gross SqFt
# nyc_condos$log_GrossSqFt <- log(nyc_condos$Gross.SqFt)
# # Log transform Estimated Gross Income
# nyc_condos$log_EstimatedGrossIncome <- log(nyc_condos$Estimated.Gross.Income)
# # Log transform Estimated Expense
# nyc_condos$log_EstimatedExpense <- log(nyc_condos$Estimated.Expense)
# Log transform Net Operating Income
nyc_condos$log_NetOperatingIncome <- log(nyc_condos$Net.Operating.Income)
nyc_condos_full$log_NetOperatingIncome <- log(nyc_condos_full$Net.Operating.Income)
train_data$log_NetOperatingIncome <- log(train_data$Net.Operating.Income)
test_data$log_NetOperatingIncome <- log(test_data$Net.Operating.Income)


nyc_condos$log_Full.Market.Value <- log(nyc_condos$Full.Market.Value)
nyc_condos_full$log_Full.Market.Value <- log(nyc_condos_full$Full.Market.Value)
train_data$log_Full.Market.Value <- log(train_data$Full.Market.Value)
test_data$log_Full.Market.Value <- log(test_data$Full.Market.Value)



nyc_condos$Net.Operating.Income.per.SqFt <- nyc_condos$Net.Operating.Income/ nyc_condos$Gross.SqFt 
nyc_condos_full$Net.Operating.Income.per.SqFt <- nyc_condos_full$Net.Operating.Income/ nyc_condos_full$Gross.SqFt 
train_data$Net.Operating.Income.per.SqFt <- train_data$Net.Operating.Income/ train_data$Gross.SqFt 
test_data$Net.Operating.Income.per.SqFt <- test_data$Net.Operating.Income/ test_data$Gross.SqFt 



# Log transform Full Market Value
# nyc_condos$log_FullMarketValue <- log(nyc_condos$Full.Market.Value)
# 
# nyc_condos$log_average_market_value <- log(nyc_condos$average_market_value)

```

```{r Variables_Selection}
#| warning: false
#| message: false
set.seed(250)
## model.matrix() creates our design matrix of predictors
x <- model.matrix(Full.Market.Value  ~ Year.Built + Total.Units + Estimated.Gross.Income + Gross.Income.per.SqFt + Estimated.Expense + Expense.per.SqFt + log_NetOperatingIncome + Gross.SqFt, nyc_condos)[,-1]
## select our outcome and convert it into a vector
## instead of a dataframe
y <- nyc_condos %>% select(Full.Market.Value) %>% unlist() %>% as.numeric()
## fit lasso for a range of lambda values (lambda is the tuning parameter
## that controls shrinkage)
cv.out <- cv.glmnet(x, y, alpha = 1)
## pick out the optimal lambda
bestlam <- cv.out$lambda.min
## get coefficients from the Lasso model
lasso <- as.matrix(coef(cv.out, s = bestlam))
t(lasso)
```

```{r MLR}

# lm <- lm(Full.Market.Value ~ Year.Built + Gross.SqFt+ Gross.Income.per.SqFt + Expense.per.SqFt + log_NetOperatingIncome, data = train_data)
# summary(lm)

lm <- lm(log_Full.Market.Value ~ Year.Built + Gross.SqFt+ Gross.Income.per.SqFt + Expense.per.SqFt + Net.Operating.Income.per.SqFt, data = train_data)
summary(lm)
```

### Our Model is:

$$
\[
\text{Market Value} = -103900000 + 8193 \times \text{Year.Built} - 4845 \times \text{Total.Units} + 107.4 \times \text{Gross.SqFt} + 553200 \times \text{Gross.Income.per.SqFt} - 515800 \times \text{Expense.per.SqFt} +  6079000 \times \log(\text{Net.Operating.Income}) + \epsilon
\]

$$

```{r K_FoldValidation}

mse.lm.i <- function(i) {
  # Split the test data into k folds
  folds <- split(test_data, 1:nrow(test_data) %% 10)
  
  # Get the test data for the current fold
  fold_test_data <- folds[[i]]
  
  # Predict on the test data for the current fold
  yhat_test <- predict(lm, newdata = fold_test_data)
  
  # Compute the MSE for the current fold
  mse_fold <- mean((fold_test_data$Full.Market.Value - yhat_test)^2)
  
  return(mse_fold)
}

mse.lm.i(5)

```



```{r UnusualPoint}


Lev <- data.frame(hatvalues(lm)) %>%
ggplot(aes(x = 1:length(hatvalues(lm)), hatvalues(lm))) +
geom_point() +
labs(title = "Leverage",
x = "x", y = "Leverage")


stdresid <- data.frame(rstandard(lm)) %>%
ggplot(aes(x = 1:length(rstandard(lm)), rstandard(lm))) +
geom_point() +
labs(title = "Standardized Residuals",
x = "x", y = "Standardized Residuals")



studresid <- data.frame(rstudent(lm)) %>%
ggplot(aes(x = 1:length(rstudent(lm)), rstudent(lm))) +
geom_point() +
labs(title = "Studentized Residuals",
x = "x", y = "Studentized Residuals")

cooks <- data.frame(cooks.distance(lm)) %>%
ggplot(aes(x = 1:length(cooks.distance(lm)), cooks.distance(lm))) +
geom_point() +
labs(title = "Cooks Distance",
x = "x", y = "Cooks Distance")



p <- length(lm$coeff)
# n <- nrow(train_data)
n <- 22102

Lev <- Lev +
geom_hline(yintercept = 2*p/n, lty = "dashed", col = "orange")

stdresid <- stdresid +
geom_hline(yintercept = 2, lty = "dashed", col = "orange")

studresid <- studresid +
geom_hline(yintercept = 3, lty = "dashed", col = "orange")

cooks <- cooks +
geom_hline(yintercept = 1, lty = "dashed", col = "orange") +
labs(title = "Case 1",
x = "x", y = "Cooks Distance")

grid.arrange(Lev, stdresid, studresid, cooks, ncol = 2)


[# high_leverage <- train_data %>% filter(hatvalues(lm) > 2* p/n)
# high_residuals <- train_data %>% filter(abs(rstandard(lm)) > 2)
# high_influence <- train_data %>% filter(cooks.distance(lm) > 1)
# 
# 
# print(high_leverage)
# print(high_residuals)
# print(high_influence)]
```

# **Title:**

## Abstract

\
\
\

## Introduction

Explanation of our variables:\
\

1.  **CondoSection**: Identification information for the condominium.

2.  **Address**: Street address of the property.

3.  **Neighborhood**: Name of the neighborhood where the property is located.

4.  **BldgClassification**: Building classification code and description indicating the property's use.

5.  **TotalUnits**: Total number of units in the building.

6.  **YearBuilt**: Year the building was constructed.

7.  **GrossSqFt**: Gross square footage of the building.

8.  **EstGrossIncome**: Estimated gross income, calculated as income per square foot multiplied by gross square footage.

9.  **GrossIncomePerSqFt**: Estimated gross income per square foot.

10. **EstimatedExpense**: Estimated expense, calculated as expense per square foot multiplied by gross square footage.

11. **ExpensePerSqFt**: Estimated expense per square foot.

12. **NetOperatingIncome**: Net operating income, calculated as estimated gross income minus estimated expense.

13. **FullMarketValue**: Current year's total market value of the property (land and building).

14. **MarketValuePerSqFt**: Market value per square foot, calculated as full market value divided by gross square footage.

15. **ReportYear**: Year of the report.

16. **Boro-Block-Lot**: Borough-Block-Lot location identifier for the property.

## Methods

## Results

## Discussion

## Conclusion

## References
